The Weakly Nonlinear Saturation of the Magnetorotational Instability

### 2014-09-19 paper/mri_paper.tex
second amplitude equation added

\beq
\begin{split}
a & \equiv \left< \mathbb{V}^\dagger \cdot \mathcal{D}\mathbb{V}^*_{11}\right> \\
c & \equiv \left< \mathbb{V}^\dagger \cdot \mathbf{N}^*_{31}\right> \\
\widetilde{c} & \equiv \left< \mathbb{V}^\dagger \cdot \widetilde{\mathbf{N}}^*_{31}\right> \\
b & \equiv \left< \mathbb{V}^\dagger \cdot \left(\mathcal{X}\mathbb{V}_{11}\right)^* \right> \\
h & \equiv \left< \mathbb{V}^\dagger \cdot \left(\widetilde{\mathcal{L}}_2\mathbb{V}_{11} \, - \, \widetilde{\mathcal{L}}_1\mathbb{V}_{21} \right)^* \right> \\
g & \equiv \left< \mathbb{V}^\dagger \cdot \mathcal{L}_{3} \mathbb{V}_{11} \right>. \\
\end{split}
\eeq

>>>>

\beq
\begin{split}
a & \equiv \left< \mathbb{V}^\dagger \cdot \mathcal{D}\mathbb{V}^*_{11}\right> \\
c & \equiv \left< \mathbb{V}^\dagger \cdot \mathbf{N}^*_{31}\right> \\
\widetilde{c} & \equiv \left< \mathbb{V}^\dagger \cdot \widetilde{\mathbf{N}}^*_{31}\right> \\
b & \equiv \left< \mathbb{V}^\dagger \cdot \left(\mathcal{X}\mathbb{V}_{11}\right)^* \right> \\
h & \equiv \left< \mathbb{V}^\dagger \cdot \left(\widetilde{\mathcal{L}}_2\mathbb{V}_{11} \, - \, \widetilde{\mathcal{L}}_1\mathbb{V}_{21} \right)^* \right> \\
g & \equiv \left< \mathbb{V}^\dagger \cdot \mathcal{L}_{3} \mathbb{V}_{11} \right>, \\
\end{split}
\eeq

but $\widetilde{c}$ is equal to zero and drops out of the equation. This is the well-known Ginzburg-Landau equation, and is with only slight modification the same amplitude equation derived in \citeauthor{Umurhan:2007hs}.

There exists a second amplitude equation, corresponding to the neutral mode, which comes from the solvability condition that must be imposed on all terms in Equation \ref{ordere3} that have no $z$ dependence. These terms are

\beq
\begin{split}
\mathcal{D}\mathbb{U}_{11} \partial_T \beta \, & = \, \mathcal{L}\mathbf{V_3} \, + \, \widetilde{\mathcal{L}}_1 \mathbb{V}_{20} 2 \left|\alpha\right| \partial_Z \alpha \, - \, \widetilde{\mathcal{L}}_1 \mathbb{U}_{20} \partial_Z^2 \beta \, \\
& + \, \widetilde{\mathcal{L}}_2 \mathbb{U}_{11} \partial_Z^2 \beta \, - \, \mathcal{X} \mathbb{U}_{11} \partial_Z \beta,
\end{split}
\eeq

and taking the inner product of these terms with the adjoint homogenous solution $\mathbb{U}_{11}$ yields

\beq
\partial_T \beta = k 2 \left|\alpha\right| \partial_Z \alpha - m \partial_Z^2 \beta + \frac{1}{\reym} \partial_Z^2 \beta - p \alpha^* \partial_Z \alpha,
\eeq

\beq
\begin{split}
n & \equiv \left< \mathbb{U}_{11} \cdot \left(\mathcal{L} \mathbb{V}_{30}\right)^*\right> \\
k & \equiv \left< \mathbb{U}_{11} \cdot \left(\widetilde{\mathcal{L}}_1 \mathbb{V}_{20}\right)^*\right> \\
m & \equiv \left< \mathbb{U}_{11} \cdot \left(\widetilde{\mathcal{L}}_1 \mathbb{U}_{20}\right)^*\right> \\
p & \equiv \left< \mathbb{U}_{11} \cdot N_{30}^*\right>, \\
\end{split}
\eeq

but both $k$ and $p$ are equal to zero, so this amplitude equation decouples from Equation \ref{ampeq1}, and reveals itself to be a simple diffusion equation,

\beq\label{ampeq2}
\partial_T \beta = - m \partial_Z^2 \beta + \frac{1}{\reym} \partial_Z^2 \beta.
\eeq
